AA Distributed Software Development Methodology

### 2013-06-02 paper.tex
ate l 155 consolidado com hybrid

There has been a large amount of research done in the area of
methodologies to deal with distributed teams of developers. We are
focusing in GSD here, however some principles involved on those
methodologies could be used on smaller teams of developers working in
the same place, time and with minor cultural differences. Moreover we
generally think on ``distributed development'' being global which is
not totally true. We even applied AA to a team that work at the same
city but on different times (more details on
Section~\ref{results}). Even smaller groups of developers working on
the same building could use GSD methodologies. A thorough survey of
these methodologies is beyond the scope of this paper. Here we present
a brief overview.

>>>>

There has been a large amount of research in methodologies to deal with
distributed teams of developers. Although this paper focuses on GSD, some of the
same
principles could also be adapted for smaller teams of
developers working at the same place, timezone and with minor cultural
differences, depending on the specific context and demands.
Moreover, `distributed development' is generally tought of as being
global which is not true. For instance, AA has been effectively applied to a team whose
members live in the same city but work at different timeframes and locations, see 
Section~\ref{results}.  Even smaller groups of developers working on the same
building could use GSD methodologies (or an adapted subset) to their benefit,
\eg, to account for different work habits, minimize formal meetings, document work
process and history, and so on. A thorough survey of these methodologies is beyond the scope
of this paper; this section presents but a brief overview.
